The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-20 analysis/paper/paper.qmd

# Load packages ----
## Managing paths
library(here)

## Data manipulation and visualisation
library(tidyverse)
library(reshape2)

## Text processing and analysis
library(tidytext)
library(SnowballC)
library(tm)
library(topicmodels)

## Working with spatial data
library(tidygeocoder)

@@

```{r}
#| label: extract-pdf-text
#| echo: false
#| cache: true

@@

```{r}
emu_theses_dtm <- emu_theses_words |> 
  count(title, word, sort = TRUE) |> 
  cast_dtm(title, word, n)

emu_theses_dtm

emu_theses_lda <- LDA(emu_theses_dtm, k = 2, control = list(seed = 2023))
emu_theses_lda

emu_theses_topics <- tidy(emu_theses_lda, matrix = "beta")
emu_theses_topics

# The top 10 words that are the most coomon in each topic
emu_theses_top_terms <- emu_theses_topics |> 
  group_by(topic) |> 
  top_n(10, beta) |> 
  ungroup() |> 
  arrange(topic, -beta)

emu_theses_top_terms |> 
  mutate(term = reorder(term, beta)) |> 
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()

# 
beta_spread <- emu_theses_topics |> 
  mutate(topic = paste0("topic", topic)) |> 
  spread(topic, beta) |> 
  filter(topic1 > 0.001, topic2 > .001) |> 
  mutate(log_ratio = log2(topic2/topic1))

beta_spread

beta_spread %>%
  group_by(direction = log_ratio > 0) %>%
  slice_max(abs(log_ratio), n = 10) %>% 
  ungroup() %>%
  mutate(term = reorder(term, log_ratio)) %>%
  ggplot(aes(log_ratio, term)) +
  geom_col() +
  labs(x = "Log2 ratio of beta in topic 2 / topic 1", y = NULL)

emu_theses_documents <- tidy(emu_theses_lda, matrix = "gamma")
emu_theses_documents
```

>>>>

# Load packages ----
## List packages to be loaded
packages <- c(
  "here",                         # Managing paths
  "tidyverse",                    # Data manipulation and visualisation
  "tidytext", "SnowballC", "tm",  # Text processing and analysis
  "tidygeocoder",                 # Working with spatial data
  "igraph", "ggraph"              # Network analysis and visualsation
)

## Load required packages, install them if needed
for (package in packages) {
  if (!require(package, character.only = TRUE)) {
    install.packages(package)
  }
  library(package, character.only = TRUE)
}

@@

```{r}
#| label: extract-pdf-text
#| echo: false

# Extract text from PDFs
# On the first run, this function might take extra time as a Python environment needs to be set up

@@
